---
title: "Tint Is Not Tufte"
subtitle: "An implementation in R Markdown"
author: "JJ Allaire, Yihui Xie, Dirk Eddelbuettel"
date: "`r Sys.Date()`"
output: tint::tintPdf
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
#library(stp25output)

 library(knitr)

knitr::opts_chunk$set(
  tidy = FALSE,
  cache.extra = packageVersion('tufte') #  kable.force.latex = TRUE
)
options(htmltools.dir.version = FALSE)
```




## Full width table

```{r, echo=FALSE}
knitr::kable(
  mtcars[1:6, 1:6], caption = 'erster')
```

This is a test. This is a test. This is a test. This is a test. This is a 
test. This is a test. This is a test. This is a test.




```{r }
knitr::kable(mtcars[1:6, 1:6], caption = 'latex'
             , format = "latex"
             )
```

This is a test. This is a test. This is a test. This is a test. This is a 
test. This is a test. This is a test. This is a test.




```{r, results='asis'}
knitr::kable(mtcars[1:6, 1:6], caption = 'html'
             , format = "html"
             )
```

This is a test. This is a test. This is a test. This is a test. This is a 
test. This is a test. This is a test. This is a test.




```{r }
knitr::kable(mtcars[1:6, 1:6], caption = 'markdown'
             , format = "markdown"
             )
```

This is a test. This is a test. This is a test. This is a test. This is a 
test. This is a test. This is a test. This is a test.




```{r }
knitr::kable(mtcars[1:6, 1:6], caption = 'pandoc'
             , format = "pandoc"
             )
```

This is a test. This is a test. This is a test. This is a test. This is a 
test. This is a test. This is a test. This is a test.




```{r , results='asis'}
knitr::kable(mtcars[1:6, 1:6], caption = 'rst'
             , format = "rst"
             )
```
