---
title: "pdf"
author: "DI Wolfgang Peter"
date: "23/02/2020"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
require(stpvers)
note<- "Auswertung für die Puplikationen in medizinische Fachzeitschriften."


#+ data, include = FALSE
dat <- data.frame(
  term = c("A", "B", "C", "D"),
  n = c(23, 14, 56, 2),
  m = c("4.7 (2.4)", "4.1 (2.3)", "8.9 (3.6)", NA),
  stringsAsFactors = FALSE
)
DF2 <-data.frame(
  term = c("A", "B", "C", "D"),
  G1_k_n = c(23, 14, 56, 2),
  G1_k_m = c("4.7 (2.4)", "4.1 (2.3)", "8.9 (3.6)", NA),
  G2_n = c(33, 35, 78, 21),
  G2_m = c("4.9 (2.7)", "4.7 (2.5)", "4.1 (5.6)", "4.2 (5.6)")
)

 

```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

```{r, echo = TRUE}
which_output()
get_my_options()$output
```
 

## Slide with R Output

```{r tab-1, echo = TRUE, results='asis'}
#dat %>% Output(caption="default", note=note) 
```

## Slide with Plot

```{r  tab-2, echo = TRUE, results='asis'}
#DF2 %>% Output(caption="default", note=note) 
```

